### 2021-08-20 paper/response_reviewers.tex

\documentclass{amsart}
\title{Fitting very flexible models \\
Response to reviewer}
\author{David W. Hogg and Soledad Villar}
\begin{document}
\maketitle

\textbf{Editor comment:} The referee for your article has provided a very thorough, and rather glowing, review of your excellent tutorial.  As you can see from the referee's comments, the referee has a few recommendations, that are largely of a minor nature, that we would like for you to consider within a revised version of your very informative and useful tutorial.

\textbf{Response:} We thank the reviewer and the editor for the kind comments about our manuscript and the improvement suggestions. We are submitting a revision addressing the suggested changes:
\begin{itemize}
    \item Added a comment on fast implementations of GPs and why one may not always be able to use them. HOGG
    \item Changed the color scheme in many of the figures to make the lines more distinguishable. SOLEDAD
    \item Added a short paragraph discussing jacknife given correlated noise. HOGG
    \item Added a comment about the equivalence of different formulations. HOGG
    \item Fixed typos.
\end{itemize}

\textbf{Reviewer comments:}
``Fitting very flexible models" by Hogg and Villar is an excellent tutorial on the use of linear models for interpolating data. The tutorial is well written, with clear language and mathematics that is not too difficult to follow (I especially commend the authors on building from simple OLS matrix equations to the more complex equations towards the end of the paper without the need for the reader to fill in many of the intermediate steps, as should be the case in a tutorial). The tutorial is accompanied by clear figures and the software used to generate the data and figures is publicly available. In sum, I am grateful that this article exists as I will certainly have research associates read it and implement its methods, and I anticipate building future lectures for classes on the material.

I recommend this tutorial for publication in PASP. In my opinion, it is suitable for publication as is, however, I have a few comments (mostly minor) and one (philosophical?) question that the authors may wish to consider before sending a resubmission.

MAJOR COMMENTS
--------------

  In addition to serving as a tutorial, the article (in my opinion) implores the reader to consider regularized least-squares fitting as a means of interpolating data. I find the arguments convincing. However, the authors also show that the methods described here reproduce a Gaussian process in the limit p goes to infinity. My question: with relatively fast implementations of GPs now available (such as those developed by Foreman-Mackey and collaborators, which the authors cite) – should readers be encouraged to use $O(n^3)$ methods when GPs can be implemented with faster calculations [at least in the 1d case that makes the bulk of this tutorial]?

\textbf{Response:} Thank your for your kind assessment of our work. We agree with your point of view regarding taking advantage of fast algorithms for GPs. Faster algorithms are preferable if available. However, the very fast Gaussian Process is only known for certain kernels and only in 1-dimension. In some cases you may want to use other basis like wavelet basis, or work in higher dimensions, like the sphere. To the best of our knowledge there is no fast implementation of GPs in the sphere. The regularized regression is a general framework.

We made a comment in the end of Section 7 of our manuscript stating this point.

\bigskip

\textbf{Reviewer comments:}
MINOR COMMENTS
--------------

  In Figure 5 the black and purple lines are difficult to distinguish. I would consider alternate colors, or, better yet different line styles to more easily identify the p = 30 and p = 73 curves.

\textbf{Response:} We changed the color scheme so the lines are distinguishable when printed in black and white.
 \bigskip

 \textbf{Reviewer comments:}
   Section 4 begins by refuting the commonly held belief that the number of parameters cannot exceed the number of data points. This (incorrect) folklore is taught because introductory statistics typically ascribes meaning to all the parameters in a model. While early exposure to nuisance parameters would likely benefit our field, the idea is complex and harder to understand than the slope of this line is equal to the gravitational constant. (Now I'm rambling) my point: $p > n$ only works well when meaning is not be ascribed to the parameters. Perhaps it is worth a footnote here to remind the reader of that point? Or perhaps not?

   \textbf{Response:} We agree with this comment and we modified the first paragraph of Section 4 to address it.

  \bigskip
 \textbf{Reviewer comments: }
   Eq 13 and 18 are equivalent (I believe), and this becomes clear from Eq. 23 and 24. Nevertheless I found the differing forms of 13 and 18 confusing the first couple of times I read through the text. It might be useful to add a note in the text or a footnote to Eq 18 stating that it is the same as Eq 13.

 \textbf{Response:} We added a sentence about the equivalence of equations after equation 18.

 \bigskip
  \textbf{Reviewer comments:} There are sigma hat's in Sect 8 that are missing their $*$

   \textbf{Response:} Fixed

 \bigskip
 \textbf{Reviewer comments:}
  Timeseries data, which the authors subtly suggest these methods are useful for by adopting $t_i$ instead of $x_i$, are often correlated over length scales that are larger than the typical separation between the observations. In this case, k=n jackknife estimates of the uncertainty are likely to underestimate the uncertainties in data gaps that are larger than the typical correlation length (which is a common occurrence in astronomical data). The authors may wish to add a note warning the reader about this.

 \textbf{Response:}
 This is a good point. We added a short paragraph about that in the relevant place.

\end{document}

### 2021-08-20 paper/main.tex
referee comments

% to-do
% -----
% - HOGG: Finish going through Acquaviva comments and incorporate / assess.
% - BOTH: Take one more look through the abstract (and title) and see what needs to be adjusted.
% - HOGG. It is a kernel even when p \ne \infty! Re-word stuff in section 7.
% - Should we do a CVMSE vs the s parameter to show that you can choose kernel parameters by CV as well? Let's start by performing an experiment in the notebook. Not for now.

@@

But recall our setting:
We are using the linear fit to interpolate the data, or de-noise the data, or predict new data.
In these contexts, we typically don't care about the parameter vector $\hat{\beta}$ itself.
We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$.
From the new test times $t_\ast$ we create the test feature matrix $X_\ast$ (by the same feature embedding functions $g_j(t)$).
The prediction $\hat{Y}_\ast$ for the $y$ values at the test locations $t_\ast$ becomes
\begin{equation}\label{eq:OLS}
    \hat{Y}_\ast = X_\ast\,(X^\top X)^{-1}\,X^\top Y
    ~.
\end{equation}
Examples of OLS applied to some toy data\footnote{The algorithm by which the toy data were made---and indeed all of the code used to make the figures for this \documentname---is available online at \url{https://github.com/davidwhogg/FlexibleLinearModels}.} are shown in \figurename~\ref{fig:ols1}.
This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch.~3).
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./OLS-under.pdf}
    \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots). Fits are shown for different values of the number of basis functions $p$; there are $n=23$ data points. Here (and in all the \figurename s to follow) we are using the Fourier basis functions in \eqref{eq:basis} and shown in \figurename~\ref{fig:basis}. The data $y_i$ were generated using a function that does not reside in the function space spanned by the basis. Here the $X_\ast$ matrices used in the predictions $\hat{Y}_\ast$ were generated from a fine grid of locations in the location coordinate $t$; the plots of the fine grid of predictions are the continuous lines. The fits with larger $p$ have more flexibility to fit the data than the fit with $p=3$, but the fit at the highest $p$ shows evidence of over-fitting.}
    \label{fig:ols1}
    \end{mdframed}
\end{figure}

@@

It is common to include a regularization that discourages the fit from making use of large amplitudes $\beta_j$.
There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which (in the form that doesn't have data weights) looks like
\begin{equation} \label{eq:ridge}
    \hat{\beta} = \arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2
    ~,
\end{equation}
where $\lambda>0$ is a regularization parameter that penalizes large values for elements $\beta_j$ of the parameter vector.
This optimization is also convex.
The ridge-regularized prediction for new data looks like
\begin{equation} \label{eq:ridge_sol}
    \hat{Y}_\ast = X_\ast\,(X^\top X + \lambda\,I)^{-1}\,X^\top Y
    ~,
\end{equation}
where $I$ is the $p\times p$ identity (see Appendix \ref{app:math}).
In the language of Bayesian inference, $\lambda$ can be seen as the inverse of a prior variance for the parameters $\beta_j$.
The salutary effect of the ridge regularization is shown in \figurename~\ref{fig:ridge}.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./ridge.pdf}
    \caption{Comparison of ordinary least-squares (OLS) and ridge-regression fits (continuous lines) to the example data (black dots). In order to illustrate the differences, we chose the $p=21$-parameter fit, which shows evidence of over-fitting at the edges of the fit range. The regularized fit looks more sensible, though it fits the individual data points less precisely. The choice of regularization parameter $\lambda$ matters; here we used $\lambda=0.1$ (chosen heuristically by hand).}
    \label{fig:ridge}
    \end{mdframed}
\end{figure}

@@

\section{Over-parameterization}\label{sec:overpar}

We are taught folklore, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
This isn't true!
Not only is it the case that we \emph{can} work at $p>n$, in many cases we \emph{should} work at $p>n$, and many real-world regressions do.
But it is true that the $p>n$ regime is indeed strange.
In the over-parameterized case, there are typically many choices for the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
\begin{equation}\label{eq:opt2}
    \hat{\beta} = \arg\min_\beta \|\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~.
\end{equation}
Technically this formulation depends on an additional assumption that the feature matrix $X$ is full rank or that the data $Y$ lie in the subspace spanned by $X$.
This is true almost always when $p>n$.
This optimization is again convex and has a unique solution, although that solution will depend on feature weights that we discuss in a moment.
%When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
The under-parameterized and over-parameterized optimization statements \eqref{eq:opt1} and \eqref{eq:opt2} can be unified into one form by considering the limit of light L2 regularization:
\begin{equation}\label{eq:opt3}
    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
    ~;
\end{equation}
in the limit, this delivers the OLS solution in either case and doesn't require the constraint in \eqref{eq:opt2} to be satisfied.

In the over-parameterized case ($p>n$), the prediction looks like
\begin{equation}\label{eq:OLS2}
    \hat{Y}_\ast = X_\ast\,X^\top (X\,X^\top)^{-1}\,Y
    ~,
\end{equation}
provided that $X\,X^\top$ is invertible (which will usually be the case).
Like \eqref{eq:OLS}, this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the point that it is making the minimum-norm choice of $\beta$ among many degenerate solutions.
Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
Note that the fits with different numbers of parameters $p$ lead to very different predictions, but they all go through the data exactly.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./OLS-over.pdf}
    \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases. There are $n=23$ data points. As in \figurename~\ref{fig:ols1}, the data points $y_i$ were generated using a function that does not precisely reside in the function space spanned by the basis. The three fits are very different, but they all go through all the data points exactly. As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Plancharel's Theorem and the use of the Fourier basis (see text).}
    \label{fig:ols2}
    \end{mdframed}
\end{figure}

@@

The OLS prediction for $p>n$ is \emph{not} affine invariant with respect to $p$-dimensional rotations or rescalings.
That is, rotations and scalings in the feature space \emph{will} affect predictions.
It behooves us to re-scale the features (the $p$ $n$-vectors of the feature matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted}, \citealt{bah2016sample}, \citealt{rauhut2016interpolation}).
We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
\begin{equation} \label{eq:weighted_sol}
    \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
    ~.
\end{equation}
This can be seen as the prediction for new data resulting from the following optimization (again, assuming the data can be interpolated):
\begin{equation} \label{eq:weighted}
    \hat{\beta} = \arg\min_\beta \|\Lambda^{1/2}\,\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~,
\end{equation}
which---in analogy to the optimizations \eqref{eq:opt2} and \eqref{eq:opt3}---can also be written as
\begin{equation}
    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
    ~.
\end{equation}
This doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
This optimization
%\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
%That right-hand-side object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
%Yes, data analysis can have this kind of geometric structure!
%}
penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.

@@

@@

The idea of jackknife resampling is that we make $k$ subsamples of the data, in each of which we have dropped (or held out) a unique fraction $1/k$ of the data.
The variance of the results (in this case the prediction $\hat{Y}_\ast$) across the jackknife samples can be transformed into an estimate of the variance of the estimator acting on the full data set.
In the most extreme form---leave-one-out jackknife---we set $k=n$.
In this case, the jackknife estimate $\hat{\Sigma}_\ast$ of the variance of the best-fit predictions $\hat{Y}_\ast$ is given by
\begin{equation}\label{eq:jackknife}
    \hat{\Sigma}_\ast = \frac{n-1}{n}\,\sum_{i=1}^n (\hat{Y}_{\ast i} - \hat{Y}_\ast)\,(\hat{Y}_{\ast i} - \hat{Y}_\ast)^\top
    ~,
\end{equation}
where $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$, and $\hat{Y}_\ast$ is the estimate made using \emph{all} the data.
The pre-factor $(n-1)/n$ in \eqref{eq:jackknife} 
%is not anything like the $1/(n-1)$ that we use when you estimate a standard variance; this difference 
comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
The square-root of the trace of this uncertainty variance $\hat{\Sigma}$ (that is, what we might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
Note the similarity between jackknife and cross-validation; it is relevant and important: These empirical estimates of uncertainty and prediction error are closely related.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./uncertainty.pdf}
    \caption{The jackknife-estimated uncertainty on an ordinary least squares fit. What is shown is the diagonal of the empirical jackknife estimate $\hat{\Sigma}$ of the variance tensor on the prediction $\hat{Y}_\ast$ of an OLS fit. In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope). The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated; the jackknife formula \eqref{eq:jackknife} compensates for those correlations.}
    \label{fig:uncertainty}
    \end{mdframed}
\end{figure}

@@

To derive the optimal solutions of the constrained optimization \eqref{eq:opt2} and similar, we use a classical result in quadratic optimization (see for instance \citealt{nocedal2006numerical}, Ch.~16):
Consider the quadratic optimization problem 
\begin{equation} \label{qp}
    \arg\min_x \frac{1}{2} x^T G\, x + x^\top c \quad \text{ subject to } A\,x=b
    ~.
\end{equation}
The first-order necessary conditions for $x^*$ to be a solution of \eqref{qp} is that there is a vector $\lambda^*$ (known as Lagrange multipliers) such that the following system of equations is satisfied:
%Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e. $AZ=0$). If $Z^\top G Z$ is positive definite then the solution of \eqref{qp} is given by the Karush-Kuhn-Tucker conditions, namely 
\begin{equation}
    \left[
    \begin{matrix}
    G & A^\top \\ 
    A & 0
    \end{matrix}\right]
    \left[
    \begin{matrix}
    x^* \\ 
    \lambda^*
    \end{matrix}\right] = 
    \left[
    \begin{matrix}
    -c \\ 
    b
    \end{matrix}\right]
    ~.
    \label{kkt}
\end{equation}
Equation \eqref{kkt} is typically known as the Karush-Kuhn-Tucker conditions (KKT). If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality.\footnote{The KKT conditions can also characterize optimality in more general cases. For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G\, Z$ is positive semidefinite the KKT conditions are sufficient for optimality. If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the underparameterized linear regression but not in the overparameterized).}

>>>>

% to-do
% -----
% - Should we do a CVMSE vs the s parameter to show that you can choose kernel parameters by CV as well? Let's start by performing an experiment in the notebook. Not for now.
% - Should we cite more in the regularized and compressed-sensing contexts?
% - Should we be more explicit about what goes wrong at high dimensions?
% - Be careful to make it make it clear that we consider cross-validation to be the only empirical method to understand overfitting; check the words we write about over-fitting to match. It isn't just about the number of parameters.

@@

But recall our setting:
We are using the linear fit to interpolate the data, or de-noise the data, or predict new data.
In these contexts, we typically don't care about the parameter vector $\hat{\beta}$ itself.
We care only about the predictions at a set of new ``test'' locations $t_\ast$, which will usually be different from the training locations $t_j$.
From the new test times $t_\ast$ we create the test feature matrix $X_\ast$ (by the same feature embedding functions $g_j(t)$).
The prediction $\hat{Y}_\ast$ for the $y$ values at the test locations $t_\ast$ becomes
\begin{equation}\label{eq:OLS}
    \hat{Y}_\ast = X_\ast\,(X^\top X)^{-1}\,X^\top Y
    ~.
\end{equation}
Examples of OLS applied to some toy data\footnote{The algorithm by which the toy data were made---and indeed all of the code used to make the figures for this \documentname---is available online at \url{https://github.com/davidwhogg/FlexibleLinearModels}.} are shown in \figurename~\ref{fig:ols1}.
This form \eqref{eq:OLS} of the prediction of new test data is called ordinary least squares (OLS). It has many good properties, some of which are encoded in the Gauss--Markov theorem.
In particular, if the noise contributions in the model given in equation \eqref{eq.model} are uncorrelated, have zero mean, and equal variances for $i=1,\ldots, n$ then the Gauss--Markov theorem states that the OLS estimator has the lowest variance within the class of unbiased estimators that are linear in $Y$ (see, for example, \citealt{esl}, Ch.~3).
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./OLS-under (1).pdf}
    \caption{Ordinary least-squares (OLS) fits (continuous lines) to a set of example data points (black dots). Fits are shown for different values of the number of basis functions $p$; there are $n=23$ data points. Here (and in all the \figurename s to follow) we are using the Fourier basis functions in \eqref{eq:basis} and shown in \figurename~\ref{fig:basis}. The data $y_i$ were generated using a function that does not reside in the function space spanned by the basis. Here the $X_\ast$ matrices used in the predictions $\hat{Y}_\ast$ were generated from a fine grid of locations in the location coordinate $t$; the plots of the fine grid of predictions are the continuous lines. The fits with larger $p$ have more flexibility to fit the data than the fit with $p=3$, but the fit at the highest $p$ shows evidence of over-fitting.}
    \label{fig:ols1}
    \end{mdframed}
\end{figure}

@@

It is common to include a regularization that discourages the fit from making use of large amplitudes $\beta_j$.
There are many options, but the simplest is ridge regression (or Tikhonov regularization or L2 regularization), which (in the form that doesn't have data weights) looks like
\begin{equation} \label{eq:ridge}
    \hat{\beta} = \arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2
    ~,
\end{equation}
where $\lambda>0$ is a regularization parameter that penalizes large values for elements $\beta_j$ of the parameter vector.
This optimization is also convex.
The ridge-regularized prediction for new data looks like
\begin{equation}\label{eq:ridge_sol}
    \hat{Y}_\ast = X_\ast\,(X^\top X + \lambda\,I)^{-1}\,X^\top Y
    ~,
\end{equation}
where $I$ is the $p\times p$ identity (see Appendix \ref{app:math}).
In the language of Bayesian inference, $\lambda$ can be seen as the inverse of a prior variance for the parameters $\beta_j$.
The salutary effect of the ridge regularization is shown in \figurename~\ref{fig:ridge}.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./ridge.pdf}
    \caption{Comparison of ordinary least-squares (OLS) and ridge-regression fits (continuous lines) to the example data (black dots). In order to illustrate the differences, we chose the $p=21$-parameter fit, which shows evidence of over-fitting at the edges of the fit range. The regularized fit looks more sensible, though it fits the individual data points less precisely. The choice of regularization parameter $\lambda$ matters; here we used $\lambda=0.1$ (chosen heuristically by hand).}
    \label{fig:ridge}
    \end{mdframed}
\end{figure}

@@

\section{Over-parameterization}\label{sec:overpar}
We are taught folklore, that we can never fit for more parameters than we have data. That is, we can never work at $p>n$.
This isn't true!
Not only is it the case that we \emph{can} work at $p>n$, in many cases we \emph{should} work at $p>n$, and many real-world regressions do.
In the over-parameterized case, there are typically many choices for the parameters $\beta_j$ that will literally zero out the differences between the data $Y$ and the linear prediction $X\,\beta$.
In the introduction we said that we are considering the case of linear regression in which \emph{we don't care about the values of the parameters}.
That is, the parameters of our linear fits are just nuisance parameters.
This means that we don't have very detailed opinions about how these redundancies in the model (redundancies that appear when $p>n$) are resolved.
The OLS solution, in this case, is defined (somewhat arbitrarily) to be the minimum-norm parameter vector $\beta$ that interpolates the data:
\begin{equation}\label{eq:opt2}
    \hat{\beta} = \arg\min_\beta \|\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~.
\end{equation}
Technically this formulation depends on an additional assumption that the feature matrix $X$ is full rank or that the data $Y$ lie in the subspace spanned by $X$.
This is true almost always when $p>n$.
This optimization is again convex and has a unique solution, although that solution will depend on feature weights that we discuss in a moment.
%When the investigator knows uncertainties on the training data points $y_i$, this expression will change a bit; we return to that in the next \sectionname.
The under-parameterized and over-parameterized optimization statements \eqref{eq:opt1} and \eqref{eq:opt2} can be unified into one form by considering the limit of light L2 regularization:
\begin{equation}\label{eq:opt3}
    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\beta\|_2^2\right]
    ~;
\end{equation}
in the limit, this delivers the OLS solution in either case and doesn't require the constraint in \eqref{eq:opt2} to be satisfied.

In the over-parameterized case ($p>n$), the prediction looks like
\begin{equation}\label{eq:OLS2}
    \hat{Y}_\ast = X_\ast\,X^\top (X\,X^\top)^{-1}\,Y
    ~,
\end{equation}
provided that $X\,X^\top$ is invertible (which will usually be the case).
Like \eqref{eq:OLS}, this prediction is \emph{also} called ordinary least squares (OLS), or sometimes ``min-norm least-squares'' to emphasize the point that it is making the minimum-norm choice of $\beta$ among many degenerate solutions.
Examples of OLS fits in the over-parameterized regime are shown in \figurename~\ref{fig:ols2}.
Note that the fits with different numbers of parameters $p$ lead to very different predictions, but they all go through the data exactly.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./OLS-over (1).pdf}
    \caption{Ordinary least-squares (OLS) or min-norm least-squares fits (continuous lines) to a set of example data points (black dots), but now for a few over-parameterized cases. There are $n=23$ data points. As in \figurename~\ref{fig:ols1}, the data points $y_i$ were generated using a function that does not precisely reside in the function space spanned by the basis. The three fits are very different, but they all go through all the data points exactly. As $p$ gets large, the fit function approaches $y=0$ almost everywhere; this is a consequence of Plancharel's Theorem and the use of the Fourier basis (see text).}
    \label{fig:ols2}
    \end{mdframed}
\end{figure}

@@

The OLS prediction for $p>n$ is \emph{not} affine invariant with respect to $p$-dimensional rotations or rescalings.
That is, rotations and scalings in the feature space \emph{will} affect predictions.
It behooves us to re-scale the features (the $p$ $n$-vectors of the feature matrix $X$) in a sensible way, like for instance, to encourage the fit to use low-frequency features more than high-frequency features (\citealt{xie2020weighted}, \citealt{bah2016sample}, \citealt{rauhut2016interpolation}).
We can encode these feature weights in a $p\times p$ diagonal weight matrix $\Lambda^{-1}$ and the prediction becomes
\begin{equation} \label{eq:weighted_sol}
    \hat{Y}_\ast = X_\ast\,\Lambda^{-1}\,X^\top (X\,\Lambda^{-1}\,X^\top)^{-1}\,Y
    ~.
\end{equation}
This equation is a special case of the fully general form we will give below in \eqref{eq:LambdaC2}, and equivalent to a special case of \eqref{eq:foo} above.
This \eqref{eq:weighted_sol} can be seen as the prediction for new data resulting from the following optimization (again, assuming the data can be interpolated):
\begin{equation} \label{eq:weighted}
    \hat{\beta} = \arg\min_\beta \|\Lambda^{1/2}\,\beta\|_2^2 ~~\mbox{subject to}~~ Y = X\,\beta
    ~,
\end{equation}
which---in analogy to the optimizations \eqref{eq:opt2} and \eqref{eq:opt3}---can also be written as
\begin{equation}
    \hat{\beta} = \lim_{\lambda\to 0^+}\left[\arg\min_\beta \|Y - X\,\beta\|_2^2 + \lambda\,\|\Lambda^{1/2}\,\beta\|_2^2\right]
    ~.
\end{equation}
This doesn't require the constraints in \eqref{eq:weighted} to be satisfied. 
This optimization
%\footnote{If you are a physicist and you don't like the mathematical $\|\cdot\|_2^2$ notation---if you prefer to look at quantities that are obvious scalar forms---then recall that $\|\Lambda^{1/2}\,\beta\|_2^2 = \beta^\top\Lambda\,\beta$.
%That right-hand-side object is a gauge-invariant object so long as $\beta$ and $\Lambda$ are also gauge-invariant objects themselves.
%Yes, data analysis can have this kind of geometric structure!
%}
penalizes more strongly the parameters $\beta_j$ corresponding to features $g_j(t)$ with larger values of $[\Lambda^{1/2}]_{jj}$.

@@

We remark that a naive implementation of the regularized regression using \eqref{eq:gpC} has an $O(n^3)$ time complexity.
However, Gaussian processes can be implemented in something close to $O(n)$ for certain classes of one-dimensional models (\citealt{ambikasaran2015fast, celerite}).
Given this, you might ask: Why use $O(n^3)$ feature-weighted over-parameterized regressions when you could just use a fast GP?
Unfortunately there are not algorithms that are so fast for higher dimensional GPs, and there are no good algorithms at all for many situations (for example GPs on the surface of a sphere).
Furthermore, the standard GP implementations focus on stationary GPs, which do not encompass all the options that one might construct with non-stationary basis functions.
Given all this, it is often the case that one should or must use linear-regression frameworks, when appropriate GPs are not available.

@@

The idea of jackknife resampling is that we make $k$ subsamples of the data, in each of which we have dropped (or held out) a unique fraction $1/k$ of the data.
The variance of the results (in this case the prediction $\hat{Y}_\ast$) across the jackknife samples can be transformed into an estimate of the variance of the estimator acting on the full data set.
In the most extreme form---leave-one-out jackknife---we set $k=n$.
In this case, the jackknife estimate $\hat{\Sigma}_\ast$ of the variance of the best-fit predictions $\hat{Y}_\ast$ is given by
\begin{equation}\label{eq:jackknife}
    \hat{\Sigma}_\ast = \frac{n-1}{n}\,\sum_{i=1}^n (\hat{Y}_{\ast i} - \hat{Y}_\ast)\,(\hat{Y}_{\ast i} - \hat{Y}_\ast)^\top
    ~,
\end{equation}
where $\hat{Y}_{\ast i}$ is the estimate of $Y_\ast$ made after \emph{leaving out} the one training point $t_i, y_i$, and $\hat{Y}_\ast$ is the estimate made using \emph{all} the data.
The pre-factor $(n-1)/n$ in \eqref{eq:jackknife} 
%is not anything like the $1/(n-1)$ that we use when you estimate a standard variance; this difference 
comes from the fact that the jackknife subsamples are extremely correlated; the pre-factor is computed to amplify the jackknife variance into an unbiased estimate of the variance of the estimator $\hat{Y}_\ast$.
The square-root of the trace of this uncertainty variance $\hat{\Sigma}_\ast$ (that is, what we might call the jackknife estimate of the standard error) is shown in \figurename~\ref{fig:uncertainty}.
Note the similarity between jackknife and cross-validation; it is relevant and important: These empirical estimates of uncertainty and prediction error are closely related.
\begin{figure}[t]
    \begin{mdframed}
    \includegraphics[width=\figurewidth]{./uncertainty.pdf}
    \caption{The jackknife-estimated uncertainty on an ordinary least squares fit. What is shown is the diagonal of the empirical jackknife estimate $\hat{\Sigma}_\ast$ of the variance tensor on the prediction $\hat{Y}_\ast$ of an OLS fit. In other words, the off-diagonal entries of $\hat{\Sigma}_\ast$ are being ignored here; there are important covariances that are hard to visualize (and beyond our scope). The one-sigma region is larger than the span of the jackknife trials; this is because the jackknife trials are strongly correlated; the jackknife formula \eqref{eq:jackknife} compensates for those correlations.}
    \label{fig:uncertainty}
    \end{mdframed}
\end{figure}

DAVID HOGG: write a couple of sentences about correlated timeseries as per refereee.

@@

To derive the optimal solutions of the constrained optimization \eqref{eq:opt2} and similar, we use a classical result in quadratic optimization (see for instance \citealt{nocedal2006numerical}, Ch.~16):
Consider the quadratic optimization problem 
\begin{equation} \label{qp}
    \arg\min_x \frac{1}{2} x^T G\, x + x^\top c \quad \text{ subject to } A\,x=b
    ~.
\end{equation}
The first-order necessary conditions for $x^*$ to be a solution of \eqref{qp} is that there is a vector $\lambda^*$ (known as Lagrange multipliers) such that the following system of equations is satisfied:
%Assume that $A$ has full row rank and let $Z$ be such that its columns form a basis for the null space of $A$ (i.e. $AZ=0$). If $Z^\top G Z$ is positive definite then the solution of \eqref{qp} is given by the Karush-Kuhn-Tucker conditions, namely 
\begin{equation}
    \left[
    \begin{matrix}
    G & A^\top \\ 
    A & 0
    \end{matrix}\right]
    \left[
    \begin{matrix}
    x^* \\ 
    \lambda^*
    \end{matrix}\right] = 
    \left[
    \begin{matrix}
    -c \\ 
    b
    \end{matrix}\right]
    ~.
    \label{kkt}
\end{equation}
Equation \eqref{kkt} is typically known as the Karush-Kuhn-Tucker conditions (KKT). If the objective function in \eqref{qp} is convex, the KKT conditions are also sufficient for optimality.\footnote{The KKT conditions can also characterize optimality in more general cases. For instance, if $A$ has full row rank and $Z$ is the nullspace of $A$, if $Z^\top G\, Z$ is positive semidefinite the KKT conditions are sufficient for optimality. If $Z^\top G\, Z$ is positive definite we also have that the solution of \eqref{qp} is unique (which is typically the case in the under-parameterized linear regression but not in the over-parameterized).}
